---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
```

# optiRum

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/optiRum)](https://cran.rstudio.com/package=optiRum) 
[![R-CMD-check](https://github.com/jumpingrivers/optiRum/workflows/R-CMD-check/badge.svg)](https://github.com/jumpingrivers/optiRum/actions)
[![Codecov test coverage](https://codecov.io/gh/jumpingrivers/optiRum/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jumpingrivers/optiRum?branch=main)
<!-- badges: end -->


## About
{optiRum} is a stable package of utilities created by Optimum Credit Ltd's analysts.It is designed to provide convenience functions, standards, and useful snippets.  Optimum Credit derives significant value from the R platform and associated community, so non-commercially sensitive functionality is made available in the spirit of reciprocity.

## Installation

The latest stable version of the package is available on CRAN, and you can get the latest development version by running:
```{r, eval = FALSE}
devtools::install_github("jumpingrivers/optiRum")
```

## Financial calcs

We have a range of financial functions that follow the Excel conventions.  

* `PV` -- present value
* `PMT` -- instalment
* `RATE` -- interest rate
* `APR` -- produces the annual compound rate needed for UK financial services

## Tax calcs (NEW)

As we've been doing more on calculating income and expenditure, we have included some generic functions that help calculate values for the UK tax system

* `taxYear` provides the year that a date would belong to. It can be overridden to use any tax year, but this provides a means for moving between changing tax values over time
* `calcNetIncome` gives the ability to calculate UK net income figures based off personal circumstances and tax tables

## Credit scoring / logistic regressions

There are functions for credit analysts and people dealing with logistic regressions:

* the logit, odds and probability functions enable the conversion from logit to probability, vice versa and anywhere in between -- great for handling glm outputs
* `scaledScore` -- this produces the scores that companies are used to working with for the assessment of credit quality
* `giniChart` and `giniCoef` -- produces a Gini chart in keeping with the Optimum style and embeds the coefficient, whilst the standalone giniCoef function allows for extracting a value or a series of values for use

## Miscellaneous

There are helper functions that reduce document development time:

* `sanitise` -- handles special characters for LaTeX documents, including situations where you have unresolved square brackets at the beginning which is great if you've used `cut2` and want to show summary stats for intervals
* `generatePDF` -- allows the production of PDFs in a one-liner
* `multiplot` -- allows the plotting of multiple charts into one area, primarily of benefit when producing figures for documents
* `pounds` -- displays values with a UK pound symbol at the front with UK decimalisation practices, this extends scales
* `thousands` -- displays values to the nearest thousand and in a condensed format that is ideal for charts, this extends scales
* `theme_optimum` -- this produces a good looking frame for charts
* `convertToXML` -- a lot of people are concerned about getting data out of XML, but it's difficult to find functions that put output data in XML, so this function takes XML functionality and wraps it neatly for such cases
* `CJ.dt` -- a cross-join function for two data.tables
* `wordwrap` = Change spaces to new lines in a string - great for plotting

## Code of Conduct

Please note that the optiRum project is released with a [Contributor Code of Conduct](http://jumpingrivers.github.io/optiRum/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
